### 2017-08-08 Paper01_EnthalpyAndCrystallization.tex
Results - Decon - draft paragraph about 5 vs 3 Tx fits in bulk and film.

@@

>>>>

It is worth noting the deconvolution fitted 5 crystallisation events for the bulk \MgZnCa, but only 3 events for the film. This occured because the bulk had 5 well defined events, where as the film was largely convoluted together. Thus unique solutions could not be obtained by the lesser \Tx$_{2}$ and \Tx$_{4}$ events of the film.

@@

For next paper on relaxation / rejuvenation.
